Making (Secure) FETCH Happen: \\ \vspace{2 mm} {\large Providing End-to-End Metadata Security for IMAP}

### 2015-04-20 paper.tex
good night paper

@@

\subsubsection{Mixing}
We can achieve metadata security while constraining mail server growth to a rate roughly consistent with the number of received messages. To do this, \project implements a mixing mechanism whereby scheduled updates do not simply push and pull a single message, but multiple messages amongst which the true action will be hidden.

>>>>

Email sizes follow a ``long tail" logarithmic distribution. Sizes below are calculated on a mailbox with a total of 77002 messages.

\includegraphics[width=\textwidth]{message-size-dist}

@@

\subsubsection{Mixing}
We can achieve metadata security while constraining mail server growth to a rate roughly consistent with the number of received messages. To do this, \project implements a mixing mechanism whereby scheduled updates push and pull not only a single message, but multiple messages among which the true target message will be disguised.

On a scheduled timer tick with action UP, \project selects MIX NUMBER messages from all messages with an entry in the current INDEX, (those being the messages that exist in CRYPTOBLOBS). It then FETCHes those messages from the server, reassigns their UNIQUE SUBJECTs, reuploads the new messages to the server, then deletes the messages that were fetched. When the messages are reuploaded, the new message is randomly inserted in with them, indistinguishable from the other messages. On a DOWN operation, a similar mixing occurs. MIX NUMBER + 1 messages are selected at random. If the message to be deleted is not among them, one of the selected messages is replaced with the message to actually be deleted. \project then fetches all MIX NUMBER + 1 messages, reassigns UNIQUE SUBJECTs, reuploads the MIX NUMBER messages that are not actually marked for deletion, then deletes all chosen messages. If there are fewer than MIX NUMBER messages to choose from, all existing messages are mixed.
